Spin canonical divisors of log stacky curves

### 2015-06-24 stacky_write_up/spin_cring.tex
added list for background

Let $\Gamma$ be a {\bf Fuchsian} subgroup, i.e. a discrete subgroup of $PSL_2(\BR)$ acting on the {\bf upper half plane} $\bh$ by fractional linear transformations. We can then consider the orbifold $\Gamma \backslash \bh$ over $\BC$. For example, in the case $\Gamma$ acts freely on $\bh$, $\Gamma \backslash \bh$ is a Riemann Surface over $\BC$. It may well be that $\Gamma \backslash \bh$ is not comapact. Defining $\Delta$ as the divisor of cusps associated to $\Gamma$, we can form a space $\Gamma \backslash \bh^*$ which is a compactification of $\Gamma \backslash \bh,$ with associated {\bf divisor of cusps} $\Delta$. We can now consider the {\bf ring of modular forms} $M(\Gamma) = \oplus_k M_k(\Gamma)$. In this paper, for general $\Gamma$, we sharply bound the degree of the generators and relations for $M(\Gamma).$ This was already answered in \cite[Chapters 7-9]{vzb:stacky} in the case that $M(\Gamma)$ has $M_{2k}(\Gamma) = 0$ for all $k \in \BZ$, that is, when $\Gamma$ has no odd weight modular forms, and we extend this to all Fuchsian subgroups $\Gamma$.

@@

Folloing Voight and Zureick-Brown, \cite{vzb:stacky}, we examine a much more general setting, generalizing Petri's theorem in many directions.
A divisor $\Delta \in d X$ is a {\bf log divisor} if $\Delta = \sum_{i}^{}P_i \in \di X,$ with all $P_i$ distinct. Let $(\sx,\Delta)$ denote a tame seperably rooted stacky curve over a field $k$ so that $X$ is the coarse space of $\sx$, as defined in \cite[Section 5.2]{vzb:stacky} so that $\di \sx = \div X \bigoplus_{i=1}^r \langle \frac{1}{e_i}P_i \rangle,$ with $e_i \in \BZ$. Let $K_\sx = K_X + \sum_{i=1}^{r}\frac{e_i-1}{e_i}P_i.$ In this case, we say $\sx$ has {\bf stabilizer order} $e_i$ at $P_i$. Call $\halfcan \in \di \sx$ a {\bf log half-canonical divisor} on $(\sx,\Delta)$, be a divisor $\halfcan \in \di \sx$ so that $2\halfcan \sim K_\sx + \Delta.$ If $X$ has genus $g$ and $\delta = \deg \Delta,$ then we say $\sx$ has signature $(g; e_1, \ldots, e_r;\delta)$. A {\bf log spin curve} is a triple $(X,\Delta,\halfcan)$ where $(X,\Delta)$ and $\halfcan$ is a log half-canonical divisor on $(\sx,\Delta)$. The central object of study in this paper is the {\bf log spin canonical ring} of $(X,\Delta,L)$ is
\begin{align*}
	R(X,\Delta,L) = \oplus_{n=0}^\infty H^0(X,nL)
\end{align*}
The main theorem of this paper is the following bound on the degree of generators and relations of arbitrary log spin canonical rings:

@@

The remainder of the paper will be primarily devoted to proving Theorem ~\ref{thm:general_generators_relations}. The idea of the proof will be to induct on the order and number of elliptic points. To this end, we first review important background in Section ~\ref{sec:background}. Then, in Section ~\ref{sec:induction}, we develop various inductive tools. In Sections ~\ref{sec:g_high}, ~\ref{sec:g_1} and ~\ref{sec:g_0}, we prove Theorem \ref{thm:general_generators_relations} in the cases that the genus $g \geq 2, g = 1$ and $g = 0$ respectively. Finally, in Section ~\ref{sec:further-questions}, we pose several questions for future research.

@@

\section{Background}
\label{sec:background}
\todo{Reference independence of base field}
Look at Spencer-Kodaira \cite{kodaira:complex-manifolds}.
\todo{edit this}

@@

\todo{definition and basic properties of best lower approximations}

\begin{lem}
\label{lem:deg1-sat-ind}
Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as
defined by O'Dorney \todo{reference this-Section 1 of Evan's paper, or preferably define it in the background section})
satisfying $h^0(X, \lfloor{D}\rfloor)\ge 1$.  Suppose $P$ is not a base-point of $dD$ for all $d\in \mathbf{N}^+$ meaning that $R_D$ has generically chosen generators (in the appropriate respective degrees)
$u, x_1, \ldots, _m$ all with $\ord_P=0$ and such that $\deg(u)=1$.  Let $D$ be generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
in degree at most $\bar{\tau}$, where all $x_i$s also satisfy $\ord_P(u)(x_i)$.  Suppose $D' = D + \frac{\alpha}{\beta} P$
for some $\alpha,\beta \in \mathbf{N}$ such that
\begin{equation}
\label{eqn:deg1_sat_ind_dim}
	h^0(X, \lfloor{dD + d\frac{\alpha}{\beta} P \rfloor}) = h^0(X,\lfloor dD
	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \; \forall d \in \mathbf{
	N} : d \ge \frac{\beta}{\alpha}.
\end{equation}
Let 
\[
	0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}
\]
be the non-negative best lower approximation.
Then 
\begin{itemize}
\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
degree $d_i$ and has a pole at $P$ of degree $c_i$

@@

\begin{lem}
\label{lem:sat-two-induction-high-genus}
Let $(\sx, \Delta, \halfcan_\sx)$ and $(\sx', \Delta, \halfcan_{\sx'})$ be log stacky curves with coarse space $(X, \Delta, L_X)$ and signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r-1}, \delta)$ respectively, with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.
Let $R_{L'} = R' = k[x]/I'= k[x_2, x_3
, x_5,\ldots, x_m]/I'$ and let $\halfcan = \halfcan' + \frac{1}{
3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X,\lfloor \halfcan'\rfloor)=0$).  
Suppose for $i \in \{2, 3\}$, $\deg x_i = i$ and $\ord_P(x_i)=0$ (which is satisfied generically in degree 2 and 3, since base-point freeness follows by Riemann-Roch).  Choose an ordering on $k[x_2, \ldots, x_m]$ that satisfies
\begin{align*}
	\ord_{x_2}(f) < \ord_{x_2}(g) \implies f \prec g.
\end{align*}
Then, the following statements hold.
\begin{enumerate}
	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3, 4\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
		_3,y_4,$ minimally generate $R$ over $R'$.
	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_4 \prec 
		y_3$
		and equip the ring $k[y_3, y_4, x]$ with the block 
		order so that $R = k[y_3, y_4, x]/I$. Let,
		\begin{align*}
			\initial_\prec(I) &= \initial_\prec(I')k[x, y_3, y_4] \\
			&+\langle y_4 x_j \mid 2 \leq j \leq m \rangle \\
			&+\langle y_4^2.\rangle
		\end{align*}
	\item[(c)] Any set of minimal generators for $I'$ together with 
		any set of relations with leading terms as in (b) minimally 
		generate $I$.
\end{enumerate}
\end{lem}

\begin{proof}
The assumptions on $g,\sigma$ imply $H^0(\sx, 3L), H^0(\sx, 4L)$ are both base point free: If $g \geq 2$ then $\deg 3L > 2g-1$ and $\deg 4L > 2g-1$, so $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free. If $g = 1$, we assume $\deg 3L \geq 2 > 2g-1$, so we also have $\deg 4L \geq 2 > 2g -1,$ so again $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free. Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord
_P(y_i) = 1$ by Riemann-Roch, and the assumptions on $\sigma$. \todo{Understand why/whether we need to cite lemma 5.4.7.}

In a fashion analogous to the proof of Lemma 
~\ref{lem:sat-three-induction-g-0}, we see 
the following is a $k$ basis for $R$ over $R'$:

@@

For any $x_j$, notice that $-\ord_P(y_4x_j)\le 1$.  If it is nonpositive, then it lies in $R_{\halfcan'}$ immediately giving us a relation with initial term $y_4x_j$.  Otherwise, 
we can choose $A_j \in k$ and $w_j\in R_{\halfcan'}$ such that $y_4x_j-A_jy_3w_j$ has no pole at $P$ and thus lies in $R_{\halfcan'}$ giving us a desired relation.  
Similarly, we can find $B, C \in k$ such that $y_4^2 + B y_3^2 x_2+ Cy_3x_2x_3$ has no pole at $P$ and is thus in $R_D$.  In both cases we induce a relation, with initial term described in the lemma's statement.  Noting that any monomial is either a multiple of one of these initial terms, is a basis element (described above), or is in $R_D$, we see that these monomials in fact generate the initial ideal of $I$ over $\initial(I')$.

@@

\begin{lem}
\label{lem:sat-three-induction-g-0}
\todo{Make explicit assumptions on genus.}
Suppose $L'$ is a log half-canonical divisor of $\sx$ with course space $X$ of genus 0 such that $sat(Eff(\halfcan')) = 3$ with $R_{\halfcan'} = k[x_3, x_4
, x_5,\ldots, x_m]/I'$.  Let $L = L' + \frac{1}{
3}P$.  Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that the ordering on $k[x]$ satisfies
\begin{align*}
	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
\end{align*}
Then, the following statements hold.

@@

\iffalse{
\begin{lem}
\label{lem:adding_points_saturation_2_to_1_with_log}
Let $(\sx, \Delta, \halfcan)$ and $(\sx, \Delta', L')$ be tame separably rooted log stacky spin 
curves with $0\ne \Delta=\Delta'+2P$ for some non-stacky point $P$ not in the support of $
\halfcan'$, meaning that $L=L'+P$.  Let $(g; e_1, \ldots, e_\tau; \delta+2)$ and $(g; e_1, 
\ldots, e_\tau, \delta)$ with $g\ge 2$ be their respective signatures.  Suppose 
$sat(Eff(\halfcan))=1$ and $sat(Eff(\halfcan'))=2$.  Further suppose $R_{\halfcan'} = k[x_2, 
x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$.  Then
\begin{enumerate}
\item[(a)] Then generic elements $y_1$ and $y_2$ in $(R_{\halfcan})_1$ and $
(R_{\halfcan})_2$ respectively, such that $-\ord_P(y_2)>0$ and $\{y_1^2, y_2\}$ is linearly 
independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
\item[(b)] Equip $k[y_1,y_2]$ with $grlex$ so that $y_2 \prec y_1$ and equip $k[y_1, y_2, 
x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_2, x_2, \ldots, x_m]/I$.  
Then
\begin{align*}
			in_\prec(I) &= in_\prec(I')k[x_2, \ldots, x_m, y_1, y_2] \\
			&+\langle y_2 x_j \mid 2 \leq j \leq m \rangle \\
			&+\langle y_2^2\rangle.
		\end{align*}
\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with 
leading terms as above minimally generate $I$.
\end{enumerate}
\end{lem}

@@

\section{High genus}
\label{sec:g_high}
We now consider the case when the genus is at least 2. In this case, we are able to bound the degrees and relations of the half canonical ring $R_L$. In this section, we do not obtain explicit presentations of $R_L.$ In contrast, in Section ~\ref{sec:g_1} and Section ~\ref{sec:g_0} we will not only obtain bounds on the generators and relations, but also obtain presentations inductively. The tradeoff is that in the cases of genus 0 and 1, we will have to explicitly deal with base cases, making the induction more involved. We begin with the case that $g \geq 2$.

@@

In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P-Q$ where $P,Q$ are distinct points, fixed under the hyperelliptic involution. We aim to inductively construct presentations by increasing the values of the $e_i$ using Theorem ~\ref{thm:ram_order_ind} and add additional points using Lemma ~\ref{lem:deg1-sat-ind} and Lemma ~\ref{lem:sat-two-induction-high-genus}.

@@

There are two main cases: when $\delta \geq 2$ and when $\delta = 0$
 (note that $\delta$ must be odd or zero because $\halfcan \in \text
{ Div } \sx$). In the first case, $\deg \lfloor \halfcan \rfloor
\geq 0$ so the result directly follows from Lemma
~\ref{lem:deg1-sat-ind}. When $\delta = 0$, this is not necessarily
true so the proof is a rather involved induction using Lemma
~\ref{lem:sat-three-induction-g-0} and Theorem ~\ref{thm:ram_order_ind}.
The remainder of this section is dedicated to characterizing the
saturations (Subsection ~\ref{ssec:g_0_saturation}), inductive
base cases (Subsection ~\ref{ssec:g_0_base}), and exceptional
cases (Subsection ~\ref{ssec:g_0_exceptional}) when $\delta = 0$
before proving the main theorem in full for all $\delta$ in
Subsection ~\ref{ssec:g_0_main}.

@@

\ssec{Base Cases}
\label{ssec:g_0_base}
Now we have an inductive statement on the number of ramified
points in Lemma ~\ref{lem:sat-three-induction-g-0} and
an inductive statement on stabilizer orders in Theorem
~\ref{thm:ram_order_ind}. After verifying that explicit pairs
$(\sx, J)$ of stacky curves $\sx$ with particular signatures and
particular choices of $J$ are admissible, the application of the
two inductive statements demonstrate that the spin canonical ring
$R(\sx , 0, L)$ is generated in degree at most $e := \max(5, e_1,
\ldots, e_r)$ with relations generated in degree at most $2e$ for
$\sx$ with any signature $\sigma = (0; e_1, \ldots , e_r; 0)$ outside
of a finite set of exceptional cases.

@@

Through the application of two processes of induction, by adding 
points via Lemma ~\ref{lem:sat-three-induction-g-0} and by raising
stabilizer orders via Theorem ~\ref{thm:ram_order_ind},
we obtain Theorem ~\ref{thm:g_0_generators_relations} for any tame
log spin curve $(\sx, \Delta, L)$ over a perfect field $k$ with
signature $\sigma$ covered by this induction process.
In particular, this induction process covers all signatures $\sigma
= (0; e_1, \ldots, e_r; 0)$ such that either $r \geq 5$ or
for some listed base case $(\sigma', J)$ with $\sigma' = (0; e_1',
\ldots, e_r'; 0)$, $e_i \geq e_i'$ for all $i$.
Before we prove the main theorem, we describe the cases not be
covered by induction.

@@

Now let us consider the case when $\delta \geq 2$. In any such case,
$\lfloor \halfcan \rfloor$ is an effective divisor and the conditions
of Lemma ~\ref{lem:deg1-sat-ind} are satisfied. Thus, we can apply
the lemma inductively on the classical case with no stacky points
to get that $R(\sx, \Delta, \halfcan)$ is generated up to degree $e$
with relations generated up to degree $2e$.

@@

If $r > 5$, then we can use Lemma
~\ref{lem:sat-three-induction-g-0} to add ramified points with
stabilizer order $3$ to case (k) of Lemma
~\ref{lem:g_0_admissible_cases}, which corresponds to $\sigma_{11}
= (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$. This case
clearly satisfies the conditions of Lemma
~\ref{lem:sat-three-induction-g-0} (recall from Subsection ~\ref
{ssec:g_0_saturation} that saturation is 3 here), and the
immediate consequence of parts (a) and (c) of Lemma
~\ref{lem:sat-three-induction-g-0} is that any $R(\sx', \Delta,
\halfcan')$ corresponding to signatures $\sigma'$ with ramification
orders all equal to $3$ for any $r > 5$ is generated up to
degree $e := \max(5, e_1', \ldots, e_r')$ with relations generated
up to degree $2e$. Furthermore, Lemma ~\ref{lem:n-3s-admissible}
implies that these cases satisfy all of the conditions of Theorem
~\ref{thm:ram_order_ind}.

@@

All such base cases satisfy all of the hypotheses of
Theorem ~\ref{thm:ram_order_ind} and their corresponding $R' :=
R(\sx', \Delta, \halfcan')$ are generated, as $k$-algebras, up
to degree $e' := \max(5, e_1', \ldots, e_r')$ with relations
generated up to degree $2e'$ by Lemma ~\ref{lem:g_0_admissible_cases}.
It follows from Theorem ~\ref{thm:ram_order_ind}(b) that $R :=
R(\sx, \Delta, \halfcan)$ is generated up to degree $e := \max(5,
e_1, \ldots, e_r)$. It follows from Theorem ~\ref{thm:ram_order_ind}
(d) that the relations are generated up to degree $2e$.
\end{proof}

\section{Further Research}
\label{sec:further-questions}
\begin{itemize}
	\item More on fractional modular forms
	\item Make explicit generators and relations for base case of non-stacky higher genus half-canonical divisors
	\item In the case $g \geq 2$, can the bound from Proposition ~\ref{prop:relations_generation} be reduced from 11 to 10 (which would then be sharp by Remark ~\ref{rem:relations_generation_ten})? \todo{Possibly think more about this} 
	\item Generic Initial ideal (and other genericness properties?)
\end{itemize}

>>>>

Let $\Gamma$ be a {\bf Fuchsian} subgroup, i.e. a discrete subgroup of $PSL_2(\BR)$ acting on the {\bf upper half plane} $\bh$ by fractional linear transformations. We can then consider the orbifold $\Gamma \backslash \bh$ over $\BC$. For example, in the case $\Gamma$ acts freely on $\bh$, $\Gamma \backslash \bh$ is a Riemann Surface over $\BC$. It may well be that $\Gamma \backslash \bh$ is not comapact. Defining $\Delta$ as the divisor of cusps associated to $\Gamma$, we can form a space $\Gamma \backslash \bh^*$ which is a compactification of $\Gamma \backslash \bh,$ with associated {\bf divisor of cusps} $\Delta$. We can now consider the {\bf ring of modular forms} $M(\Gamma) = \oplus_k M_k(\Gamma)$. In this paper, for general $\Gamma$, we sharply bound the degree of the generators and relations for $M(\Gamma).$ This was already answered in \cite[]{vzb:stacky} in the case that $M(\Gamma)$ has $M_{2k}(\Gamma) = 0$ for all $k \in \BZ$, that is, when $\Gamma$ has no odd weight modular forms, and we extend this to all Fuchsian subgroups $\Gamma$.

@@

Folloing Voight and Zureick-Brown, \cite{vzb:stacky}, we examine a much more general setting, generalizing Petri's theorem in many directions.
A divisor $\Delta \in \d X$ is a {\bf log divisor} if $\Delta = \sum_{i}^{}P_i \in \di X,$ with all $P_i$ distinct. Let $(\sx,\Delta)$ denote a tame seperably rooted stacky curve over a field $k$ so that $X$ is the coarse space of $\sx$, as defined in \cite{vzb:stacky}[Section 5.2] so that $\di \sx = \div X \bigoplus_{i=1}^r \langle \frac{1}{e_i}P_i \rangle,$ with $e_i \in \BZ$. Let $K_\sx = K_X + \sum_{i=1}^{r}\frac{e_i-1}{e_i}P_i.$ In this case, we say $\sx$ has {\bf stabilizer order} $e_i$ at $P_i$. Call $\halfcan \in \di \sx$ a {\bf log half-canonical divisor} on $(\sx,\Delta)$, be a divisor $\halfcan \in \di \sx$ so that $2\halfcan \sim K_\sx + \Delta.$ If $X$ has genus $g$ and $\delta = \deg \Delta,$ then we say $\sx$ has signature $(g;e_1,\ldots, e_r;\delta)$. A {\bf log spin curve} is a triple $(X,\Delta,\halfcan)$ where $(X,\Delta)$ and $\halfcan$ is a log half-canonical divisor on $(\sx,\Delta)$. The central object of study in this paper is the {\bf log spin canonical ring} of $(X,\Delta,L)$ is
\begin{align*}
	R(X,\Delta,L) = \oplus_{n=0}^\infty H^0(X,nL)
\end{align*}
The main theorem of this paper is the following bound on the degree of generators and relations of arbitrary log spin canonical rings:

@@

The remainder of the paper will be primarily devoted to proving Theorem ~\ref{thm:general_generators_relations}. The idea of the proof will be to induct on the order and number of elliptic points. To this end, we first review important background in Section ~\ref{sec:background}. Then, in Section ~\ref{sec:induction}, we develop various inductive tools. In Sections ~\ref{sec:g_high}, ~\ref{sec:g_1} and ~\ref{sec:g_0}, we prove Theorem \ref{thm:general_generators_relations} in the cases that the genus $g \geq 2, g = 1$ and $g = 0$ respectively. Finally, in Section ~\ref{further-questions}, we pose several questions for future research.

@@

\section{Background}
\label{sec:background}
\todo{Reference independence of base field}
Look at Spencer-Kodaira \cite{kodaira:complex-manifolds}.
Include the following:
\begin{enumerate}
	\item Note that this result is independence of base field
	\item background on grobner bases
	\item Notation $h^0 = \dim H^0$.
	\item Why we have these fractions $\frac{e_i-1}{2e_i}$ and why $e_i$ must be odd.
\end{enumerate}

@@

\begin{lem}
\label{lem:deg1_sat_ind}
Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as
defined by O'Dorney \todo{reference this-Section 1 of Evan's paper, or preferably define it in the background section})
satisfying $\deg(\lfloor{D}\rfloor)\ge 0$.  Suppose $P$ is not a base point of $D$ meaning that $R_D$ has a
generator $u$ in degree 1 that is a section of $\so_D$ with $\ord_P(u)=0$.  Let $D$ be generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
in degree at most $\bar{\tau}$.  Suppose $D' = D + \frac{\alpha}{\beta} P$
for some $\alpha,\beta \in \mathbf{N}$ such
that
\begin{equation}
\label{eqn:deg1_sat_ind_dim}
	h^0(X, \lfloor{dD + d\frac{\alpha}{\beta} P \rfloor}) = h^0(X,\lfloor dD
	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \forall d \in \mathbf{
	N} : d \ge \frac{\beta}{\alpha}.
\end{equation}
Let 
\[
	0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}
\]
be the non-negative best lower approximation.
Then 
\begin{itemize}
\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
degree $d_i$ and has a pole at $P$ of degree $c_i$

@@

\begin{lem}
\label{lem:sat-two-induction-high-genus}
Let $(\sx, \Delta, \halfcan_\sx)$ and $(\sx', \Delta, \halfcan_{\sx'})$ be log stacky curves with coarse space $(X, \Delta, L_X)$ and signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r-1}, \delta)$ respectively, with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.
Let $R_{L'} = R' = k[x]/I'= k[x_2, x_3
, x_5,\ldots, x_m]/I'$ and let $\halfcan = \halfcan' + \frac{1}{
3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X,\lfloor \halfcan'\rfloor)=0$).  Suppose $\halfcan$ and $\halfcan'$ satisfy $sat(Eff(\halfcan')) = sat(Eff(\halfcan)) = 2.$
Suppose $\deg x_i = i$ for $i \in \{2, 3\}$ and choose an ordering on $k[x_2, \ldots, x_m]$ satisfies
\begin{align*}
	\ord_{x_2}(f) < \ord_{x_2}(g) \implies f \prec g.
\end{align*}
Then, the following statements hold.
\begin{enumerate}
	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3, 4\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
		_3,y_4,$ minimally generate $R$ over $R'$.
	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_4 \prec 
		y_3$
		and equip the ring $k[y_3, y_4, x]$ with the block 
		order so that $R = k[y_3, y_4, x]/I$. Let,
		\begin{align*}
			\initial_\prec(I) &= \initial_\prec(I')k[x, y_3, y_4] \\
			&+\langle y_4 x_j \mid 2 \leq j \leq m \rangle \\
			&+\langle y_4^2.\rangle
		\end{align*}
	\item[(c)] Any set of minimal generators for $I'$ together with 
		any set of relations with leading terms as in (b) minimally 
		generate $I$.
\end{enumerate}
\end{lem}

\begin{proof}
The assumptions on $g,\sigma$ imply $H^0(\sx, 3L), H^0(\sx, 4L)$ are both base point free: If $g \geq 2$ then $\deg 3L > 2g-1$ and $\deg 4L > 2g-1$, so $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free. If $g = 1$, we assume $\deg 3L \geq 2 > 2g-1$, so we also have $\deg 4L \geq 2 > 2g -1,$ so again $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free. Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord
_P(y_i) = 1$ by Riemann Roch, and the assumptions on $\sigma$. \todo{Understand why/whether we need 
to cite lemma 5.4.7.}

In a fashion analogous to the proof of Lemma 
~\ref{lem:sat_three_induction}, we see 
the following is a $k$ basis for $R$ over $R'$:

@@

To show part (b), note that the generators in
~\ref{eqn:sat_two_add_generator} are precisely a set of monomials which
generate $k[x,y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
suffices to show that all generators of $J$ lie in $in_\prec(I)$.

This follows, since there exist constants $A_j \in k$ for $3 \leq j \leq m,$ and a constnant $B \in k$ and
elements $w_{i,j} \in R'$ so that the following linear combinations
of elements lie in $R'$.

\begin{align*}
	y_4x_j &- A_j y_3 w_j & \text{ so that } 2 \leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
	y_4^2 &+ B y_3^2 x_2 \\
\end{align*}

@@

\begin{lem}
\label{lem:sat-two-induction-genus-0}
\todo{Make explicit assumptions on genus.}
Suppose $L'$ is a log half-canonical divisor of $\sx$ with course space $X$ of genus 0 such that $sat(Eff(\halfcan')) = 3$ with $R_{\halfcan'} = k[x_3, x_4
, x_5,\ldots, x_m]/I'$.  Let $L = L' + \frac{1}{
3}P$.  Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that the ordering on $k[x]$ satisfies
\begin{align*}
	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
\end{align*}
Then, the following statements hold.

@@

\iffalse{
\begin{lem}\label{lem:adding_points_saturation_2_to_1_with_log}
Let $(\sx, \Delta, \halfcan)$ and $(\sx, \Delta', L')$ be tame separably rooted log stacky spin 
curves with $0\ne \Delta=\Delta'+2P$ for some non-stacky point $P$ not in the support of $
\halfcan'$, meaning that $L=L'+P$.  Let $(g; e_1, \ldots, e_\tau; \delta+2)$ and $(g; e_1, 
\ldots, e_\tau, \delta)$ with $g\ge 2$ be their respective signatures.  Suppose 
$sat(Eff(\halfcan))=1$ and $sat(Eff(\halfcan'))=2$.  Further suppose $R_{\halfcan'} = k[x_2, 
x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$.  Then
\begin{enumerate}
\item[(a)] Then generic elements $y_1$ and $y_2$ in $(R_{\halfcan})_1$ and $
(R_{\halfcan})_2$ respectively, such that $-\ord_P(y_2)>0$ and $\{y_1^2, y_2\}$ is linearly 
independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
\item[(b)] Equip $k[y_1,y_2]$ with $grlex$ so that $y_2 \prec y_1$ and equip $k[y_1, y_2, 
x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_2, x_2, \ldots, x_m]/I$.  
Then
\begin{align*}
			in_\prec(I) &= in_\prec(I')k[x_2, \ldots, x_m, y_1, y_2] \\
			&+\langle y_2 x_j \mid 2 \leq j \leq m \rangle \\
			&+\langle y_2^2\rangle.
		\end{align*}
\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with 
leading terms as above minimally generate $I$.
\end{enumerate}
\end{lem}

@@

\section{High genus}
\label{sec:g_high}
We now consider the case when the genus is at least 2. In this case, we are able to bound the degrees and relations of the half canonical ring $R_L$. In this section, we do not obtain explicit presentations of $R_L.$ In contrast, in Section ~\ref{sec:g_1} and Subsection ~\ref{ssec:g_0_effective} we will not only obtain bounds on the generators and relations, but also obtain presentations inductively. The tradeoff is that in the cases of genus 0 and 1, we will have to explicitly deal with base cases, making the induction more involved. We begin with the case that $g \geq 2$.

@@

In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P-Q$ where $P,Q$ are distinct points, fixed under the hyperelliptic involution. We aim to inductively construct presentations by increasing the values of the $e_i$ using Theorem ~\ref{thm:ram_order_ind} and add additional points using Lemma ~\ref{lem:deg1_sat_ind} and Proposition ~\ref{lem:sat_two_induction}.

@@

There are two main cases: when $\delta \geq 2$ and when $\delta = 0$
 (note that $\delta$ must be odd or zero because $\halfcan \in \text
{ Div } \sx$). In the first case, $\deg \lfloor \halfcan \rfloor
\geq 0$ so the result directly follows from Lemma
~\ref{rem:deg1_sat_ind}. When $\delta = 0$, this is not necessarily
true so the proof is a rather involved induction using Lemma
~\ref{lem:sat_three_ induction} and Theorem ~\ref{thm:ram_order_ind}.
The remainder of this section is dedicated to characterizing the
saturations ( Subsection ~\ref{ssec:g_0_saturation}), inductive
base cases ( Subsection ~\ref{ssec:g_0_base}), and exceptional
cases (Subsection ~\ref{ssec:g_0_exceptional}) when $\delta = 0$
before proving the main theorem in full for all $\delta$ in
Subsection ~\ref{ssec:g_0_ main}.

@@

\ssec{Base Cases}
\label{ssec:g_0_base}
Now we have an inductive statement on the number of ramified
points in Lemma ~\ref{lem:sat_three_induction} and
an inductive statement on stabilizer orders in Theorem
~\ref{thm:ram_order_ind}. After verifying that explicit pairs
$(\sx, J)$ of stacky curves $\sx$ with particular signatures and
particular choices of $J$ are admissible, the application of the
two inductive statements demonstrate that the spin canonical ring
$R(\sx , 0, L)$ is generated in degree at most $e := \max(5, e_1,
\ldots, e_r)$ with relations generated in degree at most $2e$ for
$\sx$ with any signature $\sigma = (0; e_1, \ldots , e_r; 0)$ outside
of a finite set of exceptional cases.

@@

Through the application of two processes of induction, by adding 
points via Lemma ~\ref{lem:sat_three_induction} and by raising
stabilizer orders via Theorem ~\ref{thm:ram_order_ind},
we obtain Theorem ~\ref{thm:g_0_generators_relations} for any tame
log spin curve $(\sx, \Delta, L)$ over a perfect field $k$ with
signature $\sigma$ covered by this induction process.
In particular, this induction process covers all signatures $\sigma
= (0; e_1, \ldots, e_r; 0)$ such that either $r \geq 5$ or
for some listed base case $(\sigma', J)$ with $\sigma' = (0; e_1',
\ldots, e_r'; 0)$, $e_i \geq e_i'$ for all $i$.
Before we prove the main theorem, we describe the cases not be
covered by induction.

@@

Now let us consider the case when $\delta \geq 2$. In any such case,
$\lfloor \halfcan \rfloor$ is an effective divisor and the conditions
of Lemma ~\ref{rem:deg1_sat_ind} are satisfied. Thus, we can apply
the lemma inductively on the classical case with no stacky points
to get that $R(\sx, \Delta, \halfcan)$ is generated up to degree $e$
with relations generated up to degree $2e$.

@@

If $r > 5$, then we can use Lemma
~\ref{lem:sat_three_induction} to add ramified points with
stabilizer order $3$ to case (k) of Lemma
~\ref{lem:g_0_admissible_cases}, which corresponds to $\sigma_{11}
= (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$. This case
clearly satisfies the conditions of Lemma
~\ref{lem:sat_three_induction} (recall from Subsection ~\ref
{ssec:g_0_saturation} that saturation is 3 here), and the
immediate consequence of parts (a) and (c) of Lemma
~\ref{lem:sat_three_induction} is that any $R(\sx', \Delta,
\halfcan')$ corresponding to signatures $\sigma'$ with ramification
orders all equal to $3$ for any $r > 5$ is generated up to
degree $e := \max(5, e_1', \ldots, e_r')$ with relations generated
up to degree $2e$. Furthermore, Lemma ~\ref{lem:n-3s-admissible}
implies that these cases satisfy all of the conditions of Theorem
~\ref{thm:ram_order_ind}.

@@

All such base cases satisfy all of the hypotheses of
Theorem ~\ref{thm:ram_order_ind} and their corresponding $R' :=
R(\sx', \Delta, \halfcan')$ are generated, as $k$-algebras, up
to degree $e' := \max(5, e_1', \ldots, e_r')$ with relations
generated up to degree $2e'$ by Lemma ~\ref{g_0_admissible_cases}.
It follows from Theorem ~\ref{thm:ram_order_ind}(b) that $R :=
R(\sx, \Delta, \halfcan)$ is generated up to degree $e := \max(5,
e_1, \ldots, e_r)$. It follows from Theorem ~\ref{thm:ram_order_ind}
(d) that the relations are generated up to degree $2e$.
